---
title: "Problem 1"
author: Narad Mishra
data: 09/27/2017
output: html_document
---

a.) Load the built-in dataset state into R's memory.
```{r, echo = TRUE, results='hide'}
library(datasets)
data(state)
```
b.) List the objects in your R session. Get help for the state object.

```{r}
ls()
```

```{r, results='hide',eval=FALSE}
help(state)
```

c.) What type of object is state.x77?

```{r, echo=FALSE}
class(state.x77)
```
d.) Create a new object called new.state that is a data.frame based on the data stored in state.x77.

```{r,echo=FALSE}
new.state<-as.data.frame(state.x77)
class(new.state)
```
Table 1: First few observation of new.state data
```{r,echo=FALSE}
head(new.state)
```
e.) Attach the new.state object into the search path.
```{r, echo=TRUE}
attach(new.state)
```
f.) Compute the mean of the Illiteracy vector from the new.state object, and its residual from the mean value.
```{r, echo=FALSE}
mn<-mean(new.state[,"Illiteracy"])
new.state$residual<-(Illiteracy-mn)
mn
```
Table:2 First few observations with residual included as a new column.
```{r, echo=FALSE}
head(new.state)
```
g.) Print the element of illiteracy that are greater than the median illiteracy. print the elements of Murder that are greater than its median.

* list of Illiteracy and Murder greater than their median respectively.
```{r, echo=FALSE}
md<-median(new.state[,"Illiteracy"])
up.md<-subset(new.state, Illiteracy>md)
up.md$Illiteracy

mdr.md<-median(new.state[,"Murder"])
up.mdr<-subset(new.state, Murder>mdr.md)
up.mdr$Murder

```
h.) Plot Illiteracy on the x-axis and Murder on the y-axis. From interaction wiht the graph, what 3 states have the highest murder rates?

```{r, echo=FALSE}

plot(Illiteracy,Murder,
     xlab="Illiterary", ylab="Murder")

highest<-identify(Illiteracy, Murder, 
                  labels=row.names(new.state))
```

* states with highest Murder rates are Alabama, Louisiana, Georgia.

i.) The plot function has an optional argument, type, that controls what type of plot is made (points, lines, etc). In particular, type='n' plots nothing, but sets up and draws axes and axis labels. Use this to generate a scatterplot of Illiteracy and Murder, but with the state abbreviations labeling the points, instead of the default plotting character.

```{r}
plot(Illiteracy, Murder, type='n')
text(Illiteracy, Murder, labels=state.abb)
```

j.) Write a function is.min that returns a logical vector identifying the minimum values. Write another function (call it mins) that calls is.min and returns the numerical indices of hte minimum values. Apply mins to the illiteracy vector.
```{r, echo=FALSE}
is.min<- function(x){
  z<-character(length(x))
  z<-Illiteracy %in% min(Illiteracy)
  print(z)
}
```

```{r}
is.min(Illiteracy)
```
```{r,echo=FALSE}
mins<- function(x){
   z<-which(is.min(x)==TRUE)
  return(z)
}
```
```{r}
mins(Illiteracy)
```

* The code below give us the minimum value of Illiteracy.

```{r}
Illiteracy[mins(Illiteracy)]
```
